---
title: "Trash"
author: "Ben"
date: "2023-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## My First Section

We will plot the function $f(x)=3x$ below.


```{r}
f <- function(x){3*x}
x <- seq(-4,7,0.1)
plot(x,f(x), type = "l")
```

## Second Section

Let's evaluate the function $h(x) = \sqrt{3-x}$ at $x=-4$ and $x=5$.

```{r}
h <- function(x){sqrt(3-x)}
h(-4)
h(5)
```

Notice that $h(5)$ is not defined (as $3-5<0$), which is why NANs was produced above. 

## In class functions
We'll not work on evaluating a few functions.

The first function is $w(v) = v^2 - 5v -6$. 
Let's define the function, and then evaluate it at various values.

```{r}
w <- function(v){v^2 - 5*v -6}
w(-1)
w(-3)
w(6)
w(4)
```

The second function is $f(x) = \frac{2x+4}{x^2}$. 
Let's define the function, and then evaluate it at various values.

```{r}
f <- function(x){
  ifelse(x < -1, x^3, 
         ifelse( x == -1,NaN,
                 ifelse(x < 4, 0*x-2, 
                        sqrt(x))))
}
f(-10:10)
```




